Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-06 doc/main_jfm.tex
updates

\begin{equation}
\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratio of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
  \caption{Comparison of the target angle $\Theta(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method. The schematic of the simulation setup is shown in the inset of the figure.
  }
    \label{figure1}
\end{figure}

@@

In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
the vesicle is about $8.5$ length units.
The starting center of mass position of the vesicle is pinned at the origin and we track particle velocities 
to determine the initial configuration for later use such as single and multiple vesicle simulations. This will prevent some numerical instability issues when the minimum of the total energy is not achieved. For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
Figure~\ref{figure2}(a) shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$. In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property
of the model. This implies that a local energy minimum and the equilibrium configuration are nearly attained.
The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run.

@@

For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate $\chi$ is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
\begin{align}
  \chi = \dot\gamma \cdot\frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.

@@

% needs to add more details about inclination angle, tank-treading frequency, repulsion, ...etc.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{Slip.eps}
\end{center} 
  \caption{For the shear rate $\dot\gamma=0.005$, the inter-monolayer slip is be observed. The curve in black represents the mean angle between each particle pair where the angle is calculated from the relative position of particles using the vesicle center of mass position. The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$.
  }
    \label{figure5}
\end{figure}

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c}
\hline\hline                    
Case $i$ & $\dot\gamma$ & $b_i$\\
\hline 
1 & 0.020 &  5.1648  \\
2 & 0.025 &  5.2027  \\ 
3 & 0.050 &  5.1944   \\ [1ex]
\hline    
\end{tabular} 
\label{table1}
\end{table}

@@

%\begin{figure}
%\centering
%\includegraphics[width=0.24\textwidth]{N116_shear_vel_0.pdf}
%\includegraphics[width=0.24\textwidth]{N116_shear_vel_3000.pdf}
%\includegraphics[width=0.24\textwidth]{N116_shear_vel_6000.pdf}
%\includegraphics[width=0.24\textwidth]{N116_shear_vel_9000.pdf}
%  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
%    \label{figure8}
%\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2.in]{N116_ext_0.pdf}
\includegraphics[height=2.in]{N116_ext_2000.pdf}\\
\includegraphics[height=2.in]{N116_ext_4000.pdf}
\includegraphics[height=2.in]{N116_ext_6500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple.
  }
    \label{figure8}
\end{figure}

%\begin{figure}
%\centering
%\includegraphics[width=0.24\textwidth]{N116_ext_vel_0.pdf}
%\includegraphics[width=0.24\textwidth]{N116_ext_vel_2500.pdf}
%\includegraphics[width=0.24\textwidth]{N116_ext_vel_5000.pdf}
%\includegraphics[width=0.24\textwidth]{N116_ext_vel_7500.pdf}
%  \caption{(a)-(d) The background arrows indicate the fluid velocities. }
%    \label{figure6}
%\end{figure}

@@

>>>>

\begin{equation}
\Theta(t) = \tan^{-1}\left(\frac{a}{b}\tan \left(\frac{ab \dot\gamma t}{a^2+b^2}\right)\right),
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, and the test aspect ratios of the particle are $2$ and $3$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from the Jeffery orbits.

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{JefferyOrbit2.eps}
\includegraphics[width=0.4\textwidth]{JefferyOrbit3.eps}
  \caption{Comparisons of the target angle $\Theta(t)$ versus time $t$ between the theoretical Jeffery orbit with $\dot\gamma=0.1$ and the result from the integral equation method. The schematic of the simulation setup is shown in the inset of the figure. Here two cases of aspect ratio are validated, $a/b = 2$ and $a/b=3$.
  }
    \label{figure1}
\end{figure}

@@

In order to examine the dynamics of the Janus-vesicle using the HAP coupling with hydrodynamics interactions, for the target bilayer, a circular initial shape is chosen to perform the relaxation run. 
This vesicle-like structure consists of $N=58$ disks with particle radius $r=0.5$ and the starting diameter of 
the vesicle is about $8.5$ length units.
The starting center of mass position of the Janus-vesicle is pinned at the origin and particle velocities are tracked to determine the initial configuration for later use such as single and multiple vesicle simulations. 
This will prevent some numerical instability issues when the minimum of the total energy is not achieved. 
For instance, the dynamics of the bilayer under a shear flow may reach different outcomes.
Figure~\ref{figure2}(a) shows that the magnitudes of mean velocity components ${\bf v}=\{v_x,v_y\}$ decrease exponentially with an approximation decaying rate $\sim0.005$. In the same figure, the variation of the mean particle orientation $\theta$ also decreases over a period of time as expected from the self-assembly property of the model. This implies that a local energy minimum and the equilibrium configuration are 
nearly attained. 
The time step size $\Delta t=0.2$ is used for all simulations in this work including the relaxation run.
Figure~\ref{figure2}(b) shows the configuration difference between starting and ending frames in the relaxation run. The Figure~\ref{figure2}(c)-(d) demonstrate the fluid pressure profile of two configurations. The pressure inside the permeable Janus-vesicle decreases as expected.

@@

For the $N$-body Janus-vesicle, we denote a constant initial radius $R_0=\sqrt{A_0/4\pi}$ with initial area $A_0$ and the dimensionless shear rate $\chi$ is referred from~\cite{Finken08} and~\cite{Shaqfeh11},
\begin{align}
  \chi = \dot\gamma \frac{\mu R_0^2}{\kappa},
\end{align}
%
where $\dot\gamma$ the dimensional shear rate, and $\mu$ the fluid viscosity.

@@

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.8\textwidth]{Slip.eps}
\end{center} 
  \caption{The schematic of the intermonolayer slip over a period of time. Taking shear rate $\dot\gamma=0.005$ as an example, we denote the mean angle between each particle pair $\theta(t)$ where the angle is calculated from the relative position of particles using the vesicle center of mass position. The configuration plots have two fixed particles marked in yellow and blue and labeled with the corresponding time $t=\{2000,5200,9000\}$. The midplane curve is denoted as $\Sigma_M$.
  }
    \label{figure5}
\end{figure}

\begin{table}
\caption{Friction Coefficients}
\centering    
\begin{tabular}{c c c c}
\hline\hline                    
Case $i$ & $\chi_i$ & $b_i$\\
\hline 
1 & 0.020 &  5.1648  \\
2 & 0.025 &  5.2027  \\ 
3 & 0.050 &  5.1944   \\ [1ex]
\hline    
\end{tabular} 
\label{table1}
\end{table}

@@

@@

\begin{figure}
\centering
\includegraphics[height=2.in]{N116_ext_0.pdf}
\includegraphics[height=2.in]{N116_ext_2000.pdf}\\
\includegraphics[height=2.in]{N116_ext_4000.pdf}
\includegraphics[height=2.in]{N116_ext_6500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
  }
    \label{figure8}
\end{figure}

@@

\todo[inline]{Make figure of the paths of the two centroids....}
